---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# helpeR

<!-- badges: start -->
[![R-CMD-check](https://github.com/jonotuke/helpeR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jonotuke/helpeR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of helpeR is to store the regular functions that I use. 

## Installation

You can install the development version of helpeR like so:

``` r
 remotes::install_github("jonotuke/helpeR")
```

## Adding a function

1. Use
```{r, eval=FALSE}
use_r("new_function")
```
to add function.   
2. Add in code and driver run until working.   
3. Add Roxygen.  
4. Run
```{r, eval=FALSE}
document()
```
to update document.    
5. Run
```{r, eval=FALSE}
check()
```
to check package is fine.    
6. Run 
```{r, eval=FALSE}
build()
```
to install. 


If using dplyr, you may get a `no visible binding` error. Add this to file
```{r, eval=FALSE}
utils::globalVariables(
  c("missing var")
)
```

## Adding instructions
All of the instructions are in the vignettes. 

## Adding raw-data
Set up with
```{r, eval=FALSE}
usethis::use_data_raw("grading-data")
```

## Adding extra files
These all go into `inst`, so we create this
```{r, eval=FALSE}
fs::dir_create("inst")
```
We can then get files with 
```{r, eval=FALSE}
fs::path_package("helpeR", "inst", "grading", "sc2024-gradebook.csv")
```

## Adding site
To get the site, run
```{r, eval=FALSE}
devtools::build_readme()
pkgdown::build_site()
```

## Adding a vignette
First we create the file with
```{r, eval=FALSE}
use_vignette("grading", title = "Functions to finalise marks")
```
Add notes and compile. 
