---
title: "Creating ICS files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating ICS files}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, warning=FALSE}
library(helpeR)
```

These functions are used to create ICS files so can add weeks of semester to calendar. 

The first is 

```{r, message=FALSE}
library(lubridate)
create_event(name = "Test", today())
```

This creates an all day event with the given name. If you want to export this, then you use

```{r, eval=FALSE}
create_event(name = "Test", today(), file = "test.ics")
```

Next, we can create a tibble of dates and weeks for a semester. 

```{r}
sem <- create_semester(today(), weeks = 12, MSB = 8)
sem
```

This gives a week for each row, with the date. Not that we can add a two-week MSB. 

Finally to get the calendar for a whole semester, we run

```{r}
create_cal(sem)
```

